### 2018-07-17 ident/docs/draft_4.tex

>>>>

	\begin{figure}[!tbhp]
		\centering{\includegraphics[width=1\textwidth,height=.8\textheight,keepaspectratio]{figures/summary_fig/all_flux_exp_ident}}
		\caption{The frequency and occurrence of each experiment that produce data sets that can identify each parameter in each of the four fluxes a) $v_1$, $v_2$, $v_5$ and b) $v_3$ in the small metabolic network are shown.}\label{fig:ident-expt}
	\end{figure}
